Details of specific functions

### 2020-07-16 inst/gitbook/03_specific-tutorials.Rmd
book update

```{r}
## The results as a dispRity object
example_test

@@

## Plotting the results with some classic options from plot
plot(disparity_time_slices, col = c("blue", "orange", "green"),
    ylab = c("Some measurement"), xlab = "Some other measurement",
    main = "Many options...", ylim = c(5, 0), xlim = c(4, 0))

@@

## Plotting the continuous disparity with a fixed y axis
plot(disparity_time_slices, ylim = c(1, 4))
## Adding the discrete data
plot(disparity_time_bins, type = "line", ylim = c(1, 4),
     xlab = "", ylab = "", add = TRUE)

@@

```{r}
par(mfrow = c(2,1))
## Default plotting
plot(disparity_time_slices, main = "Disparity through time")
## Plotting with more arguments
plot(disparity_time_slices, type = "preview",
     main = "Two first dimensions of the trait space")
```

>>>>

```{r, fig.height = 16, fig.width = 6}
## The results as a dispRity object
example_test

@@

## Plotting the results with some classic options from plot
plot(disparity_time_slices, col = c("blue", "orange", "green"),
    ylab = c("Some measurement"), xlab = "Some other measurement",
    main = "Many options...", ylim = c(10, 0), xlim = c(4, 0))

@@

## Plotting the continuous disparity with a fixed y axis
plot(disparity_time_slices, ylim = c(3, 9))
## Adding the discrete data
plot(disparity_time_bins, type = "line", ylim = c(3, 9),
     xlab = "", ylab = "", add = TRUE)

@@

```{r, fig.height = 16, fig.width = 8}
par(mfrow = c(2,1))
## Default plotting
plot(disparity_time_slices, main = "Disparity through time")
## Plotting with more arguments
plot(disparity_time_slices, type = "preview",
     main = "Two first dimensions of the trait space")
```
